Figures to insert in text

### 2018-04-11 Chapters/Chapter01.tex
Hathor: minor text update.

In this paper, we will analyze the network scaling and security. How a Hathor network scales, simulating different loads and measuring the bandwidth, computational effort, and storage space necessary to handle all the transactions in time. What is the minimum transaction's aggregated weight which it may be considered unlikely to be reversed?

We are interested in how the rate of new transactions affects how long it takes to a new transaction to be confirmed for the first time. We had already run some simulations under normal load (Fig. \ref{fig-tangle-hist}) and high load (Fig. \ref{fig-tangle-hist-2}).

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{./images01/fig-tangle-hist.png}
\caption{Histogram of how long has been a transaction waiting until its first confirmation. It was a simulation of 15 minutes with new transactions rate changing between 1 and 15 tx/s.\label{fig-tangle-hist}}
\end{figure}

\begin{figure}[ht]
\centering\includegraphics[width=\textwidth]{./images01/fig-tangle-hist-2.png}
\caption{Histogram of how long has been a transaction waiting until its first confirmation. It was a simulation of 5 minutes with new transactions rate of 50 tx/s, i.e., very high load.\label{fig-tangle-hist-2}}
\end{figure}

Besides the time to the first confirmation, it is also important to measure how long it takes to a new transaction reach a specific accumulated weight. It is useful for exchanges and merchants to set their minimum requirements. Bitcoin's exchanges and merchants usually requires a minimum of 6 confirmations blocks.

@@

%\cite{tangle2016} suggests that constraining transactions' weight in a range would both prevent spam, because it would be necessary a minimum work to propagate a new transaction, and attacks, because an attacker would not be allowed to propagate a transaction with very high weight. We agree with the spam argument, and would like how a minimum weight would affect mobile devices's new transactions. We partially agree with the upper bound, because an attacker would be able to generate many transaction with lower weight. We will analyze if constraining transactions' weight would be effective against nuclear submarine attacks.

%We have another suggestion to prevent nuclear submarine attacks: set a maximum depth for the transactions confirmed by a new transaction. So, new transactions would have to confirming newer transactions instead of old transactions, and a nuclear submarine attack would be controlled because the attacker would be not be able to create a large separate DAG. But the maximum depth rule would possibly also affect transaction created by low (hash)power devices, because it would take a longer time to solve the proof-of-work and, if the confirmations are going fast, the transaction would possibly be invalidated. This raises another important question: what would be an optimal maximum depth allowed?

%If we would like to include fee transactions, how would it be distributed between confirmations? As transactions may have multiple direct confirmations, it is not obvious who would receive the transaction fee. An intuitive suggestion would be to give the fee to the first confirmation with a minimum weight, but it might have some propagation problems, because it takes a while to propagate a transaction in the network and there would be conflict.

%In order to solve the fee distribution problem, we will simulate how the network would behave if we include blocks. These blocks would be like Bitcoin's, with an adjustable proof-of-work according to the network's hashpower. They would receive the fees from all confirmed transactions which had not been confirmed by any block before, and they would be able to generate new coins. These blocks would also help solving other problems.

>>>>

@@

%In this paper, we will analyze the network scaling and security. How a Hathor network scales, simulating different loads and measuring the bandwidth, computational effort, and storage space necessary to handle all the transactions in time. What is the minimum transaction's aggregated weight which it may be considered unlikely to be reversed?

%We are interested in how the rate of new transactions affects how long it takes to a new transaction to be confirmed for the first time. We had already run some simulations under normal load (Fig. \ref{fig-tangle-hist}) and high load (Fig. \ref{fig-tangle-hist-2}).

%\begin{figure}[ht]
%\centering\includegraphics[width=\textwidth]{./images01/fig-tangle-hist.png}
%\caption{Histogram of how long has been a transaction waiting until its first confirmation. It was a simulation of 15 minutes with new transactions rate changing between 1 and 15 tx/s.\label{fig-tangle-hist}}
%\end{figure}

%\begin{figure}[ht]
%\centering\includegraphics[width=\textwidth]{./images01/fig-tangle-hist-2.png}
%\caption{Histogram of how long has been a transaction waiting until its first confirmation. It was a simulation of 5 minutes with new transactions rate of 50 tx/s, i.e., very high load.\label{fig-tangle-hist-2}}
%\end{figure}

%Besides the time to the first confirmation, it is also important to measure how long it takes to a new transaction reach a specific accumulated weight. It is useful for exchanges and merchants to set their minimum requirements. Bitcoin's exchanges and merchants usually requires a minimum of 6 confirmations blocks.

%OLD \cite{tangle2016} suggests that constraining transactions' weight in a range would both prevent spam, because it would be necessary a minimum work to propagate a new transaction, and attacks, because an attacker would not be allowed to propagate a transaction with very high weight. We agree with the spam argument, and would like how a minimum weight would affect mobile devices's new transactions. We partially agree with the upper bound, because an attacker would be able to generate many transaction with lower weight. We will analyze if constraining transactions' weight would be effective against nuclear submarine attacks.

%OLD We have another suggestion to prevent nuclear submarine attacks: set a maximum depth for the transactions confirmed by a new transaction. So, new transactions would have to confirming newer transactions instead of old transactions, and a nuclear submarine attack would be controlled because the attacker would be not be able to create a large separate DAG. But the maximum depth rule would possibly also affect transaction created by low (hash)power devices, because it would take a longer time to solve the proof-of-work and, if the confirmations are going fast, the transaction would possibly be invalidated. This raises another important question: what would be an optimal maximum depth allowed?

%OLD If we would like to include fee transactions, how would it be distributed between confirmations? As transactions may have multiple direct confirmations, it is not obvious who would receive the transaction fee. An intuitive suggestion would be to give the fee to the first confirmation with a minimum weight, but it might have some propagation problems, because it takes a while to propagate a transaction in the network and there would be conflict.

%OLD In order to solve the fee distribution problem, we will simulate how the network would behave if we include blocks. These blocks would be like Bitcoin's, with an adjustable proof-of-work according to the network's hashpower. They would receive the fees from all confirmed transactions which had not been confirmed by any block before, and they would be able to generate new coins. These blocks would also help solving other problems.
